Attack-Tolerant Networks: A Structural, Multipath Approach

### 2016-08-02 wsdm-2017/source/paper.tex
Add WSDM 2017 manuscript.

%\documentclass[prodmode]{acmsmall-ec16}
%\documentclass[prodmode,license]{acmsmall-ec16}
\documentclass[prodmode,permissions]{acmsmall-ec16}

% Package to generate and customize Algorithm as per ACM style
\usepackage[ruled]{algorithm2e}
\renewcommand{\algorithmcfname}{ALGORITHM}
\usepackage{amsmath,amsfonts,amssymb,bbm} 
\usepackage[numbers,sort&compress]{natbib} % for citet
\SetArgSty{textrm}  % for algorithm2e
\SetAlFnt{\small}
\SetAlCapFnt{\small}
\SetAlCapNameFnt{\small}
\SetAlCapHSkip{0pt}
\IncMargin{-\parindent}

%\conferenceinfo{EC'16,}{July 24--28, 2016, Maastricht, The Netherlands.}
%\CopyrightYear{2016}
%\crdata{978-1-4503-3936-0/16/07}
%\copyrighttext{Copyright is held by the owner/author(s). Publication rights licensed to ACM.}

\doi{XXXXXXX.XXXXXXX}% TeXSupport

\usepackage{tikz}
\usetikzlibrary{arrows,chains,decorations.pathreplacing}
\newcommand{\beq}{\begin{eqnarray}}
\newcommand{\eeq}{\end{eqnarray}}
\DeclareMathOperator{\wbf}{wBF}

% Document starts
\begin{document}

% Page heads
%\markboth{G. Zhou et al.}{A Multifrequency MAC Specially Designed for WSN Applications}

% Title portion
\title{
Attack-Tolerance in Structured Networks via Multipath Routing
}
\author{EDWARD L. PLATT
\affil{University of Michigan}
DANIEL M. ROMERO
\affil{University of Michigan}}

\begin{abstract}
Networks with single points of failure are particularly susceptible
to adversarial faults,
in which an attacker creates faults strategically at central points.
Centralized network architectures necessarily exhibit this vulnerability,
leading to a growing popularity in decentralized architectures.
However, decentralized architectures do not guarantee the absence of single
points of failure, and networks such as the Internet and World-Wide Web have
been shown theoretically and historically to be highly susceptible to
adversarial faults.
We develop a partial trust model which makes weaker transitivity
assumptions than common web of trust models.
Using this model, we propose a general multipath fault tolerance technique for
structured networks which
provides asymptotic security against adversarial faults.
We also provide a specific algorithm for implementing this technique on the
butterfly network topology.
When network topology can be dictated, these results can be used to create scalable, attack-tolerant infrastructures.
More generally, our results provide a formalism for evaluating the effects
of network structure on adversarial fault tolerance.
\end{abstract}

%ACM is moving forward with the 2012 Classification system: http://dl.acm.org/ccs_flat.cfm. Please generate the CCSXML tex code through the online interactive system and insert the code below.

\begin{CCSXML}
<ccs2012>
<concept>
<concept_id>10002978.10002986</concept_id>
<concept_desc>Security and privacy~Formal methods and theory of security</concept_desc>
<concept_significance>500</concept_significance>
</concept>
<concept>
<concept_id>10003033.10003034</concept_id>
<concept_desc>Networks~Network architectures</concept_desc>
<concept_significance>500</concept_significance>
</concept>
<concept>
<concept_id>10011007.10010940.10010971.10010972.10010540</concept_id>
<concept_desc>Software and its engineering~Peer-to-peer architectures</concept_desc>
<concept_significance>500</concept_significance>
</concept>
</ccs2012>
\end{CCSXML}

@@

%\terms{Design, Algorithms, Performance}

\keywords{
censorship,
decentralization,
fault tolerance,
multipath,
networks,
peer-to-peer,
trust
}

\begin{bottomstuff}
%This work is supported by TODO.
Author's addresses: E.L. Platt and D.M. Romero, School of Information; email: \{elplatt,drom\}@umich.edu.
\end{bottomstuff}

\maketitle

%TODO:\\
%Fix bibtex encoding\\
%Move secrecy section\\
%Update intro to make significance more clear\\
%Clarify identifying fault\\

@@

\begin{figure}
\centerline{\includegraphics[height =.4 \textwidth]{fig-alice_trusted_neigh2}}
\caption{
Illustration of the {\em partial trust} model.
Edges represent direct, mutual trust relationships.
Alice ($v$) trusts all nodes less than
$h$ hops away---her {\em trusted neighborhood} $T_h(v)$.
Beyond that, the nodes at distance $h$ form her {\em trust boundary} $B_h(v)$.
We assume adversaries are unable to compromise nodes in the trusted neighborhood.
By compromising all nodes in the trust boundary, an adversary can ensure that
all communications leaving Alice's trusted neighborhood are compromised.
}
\label{fig:trust-source}
\end{figure}

@@

\begin{figure}
\centerline{\includegraphics[height =.4 \textwidth]{fig-bob_Alice_trusted_neigh2}}
\caption{
Partial trust model with sender (Alice) and receiver (Bob).
If disjoint paths exist connecting each node in Alice's trust boundary to
a node in Bob's,
than an adversary needs to compromise at least $|T_h(v)|$ nodes to
compromise all possible paths between Alice and Bob.
}
\label{fig:trust-source-destionation}
\end{figure}

@@

\begin{table}%
\tbl{Butterfly Multipath Routing Variables\label{tab:routing}}
{
\begin{tabular}{|l|l|}
\hline
NAME & VARIABLE \\\hline
butterfly dimension & $m \in \mathbb{Z}_+$ \\\hline
node level & $l \in \mathbb{Z} : 0 \leq l < m$ \\\hline
node place within level & $z \in \mathbb{Z}_2^m$ \\\hline
trust radius & $h \in \mathbb{Z} : 1 \leq h \leq \lfloor m/2 \rfloor$ \\\hline
path index & $s \in \mathbb{Z}_2^h$ \\\hline
\end{tabular}
}
\end{table}%

@@

% Acknowledgments
\begin{acks}
\end{acks}

% Bibliography
\bibliographystyle{ACM-Reference-Format-Journals}
\bibliography{paper}

\end{document}

>>>>

\documentclass{sig-alternate-05-2015}

%\usepackage[ruled]{algorithm2e}
%\renewcommand{\algorithmcfname}{ALGORITHM}
%\usepackage{amsmath,amsfonts,amssymb,bbm} 
%\usepackage[numbers,sort&compress]{natbib} % for citet
%\SetArgSty{textrm}  % for algorithm2e
%\SetAlFnt{\small}
%\SetAlCapFnt{\small}
%\SetAlCapNameFnt{\small}
%\SetAlCapHSkip{0pt}

\usepackage{tikz}
\usetikzlibrary{arrows,chains,decorations.pathreplacing}
%\usepackage{draftwatermark}
%\SetWatermarkText{DRAFT}
\newcommand{\beq}{\begin{eqnarray}}
\newcommand{\eeq}{\end{eqnarray}}
\DeclareMathOperator{\wbf}{wBF}

\begin{document}

% Copyright
\setcopyright{acmcopyright}
%\setcopyright{acmlicensed}
%\setcopyright{rightsretained}
%\setcopyright{usgov}
%\setcopyright{usgovmixed}
%\setcopyright{cagov}
%\setcopyright{cagovmixed}

% DOI
%\doi{10.475/123_4}

% ISBN
%\isbn{123-4567-24-567/08/06}

%Conference
\conferenceinfo{WSDM '17}{February 6--10, 2017, Cambridge, UK, USA}

\acmPrice{\$15.00}

%
% --- Author Metadata here ---
%\conferenceinfo{WOODSTOCK}{'97 El Paso, Texas USA}
%\CopyrightYear{2007} % Allows default copyright year (20XX) to be over-ridden - IF NEED BE.
%\crdata{0-12345-67-8/90/01}  % Allows default copyright data (0-89791-88-6/97/05) to be over-ridden - IF NEED BE.
% --- End of Author Metadata ---

\title{Attack-Tolerant Networks: A Structural, Multipath Approach}
%
% You need the command \numberofauthors to handle the 'placement
% and alignment' of the authors beneath the title.
%
% For aesthetic reasons, we recommend 'three authors at a time'
% i.e. three 'name/affiliation blocks' be placed beneath the title.
%
% NOTE: You are NOT restricted in how many 'rows' of
% "name/affiliations" may appear. We just ask that you restrict
% the number of 'columns' to three.
%
% Because of the available 'opening page real-estate'
% we ask you to refrain from putting more than six authors
% (two rows with three columns) beneath the article title.
% More than six makes the first-page appear very cluttered indeed.
%
% Use the \alignauthor commands to handle the names
% and affiliations for an 'aesthetic maximum' of six authors.
% Add names, affiliations, addresses for
% the seventh etc. author(s) as the argument for the
% \additionalauthors command.
% These 'additional authors' will be output/set for you
% without further effort on your part as the last section in
% the body of your article BEFORE References or any Appendices.

\numberofauthors{1} %  in this sample file, there are a *total*
% of EIGHT authors. SIX appear on the 'first-page' (for formatting
% reasons) and the remaining two appear in the \additionalauthors section.
%
\author{
% You can go ahead and credit any number of authors here,
% e.g. one 'row of three' or two rows (consisting of one row of three
% and a second row of one, two or three).
%
% The command \alignauthor (no curly braces needed) should
% precede each author name, affiliation/snail-mail address and
% e-mail address. Additionally, tag each line of
% affiliation/address with \affaddr, and tag the
% e-mail address with \email.
%
% 1st. author
\alignauthor
Anonymized Authors
}
%       \affaddr{Institute for Clarity in Documentation}\\
%       \affaddr{1932 Wallamaloo Lane}\\
%       \affaddr{Wallamaloo, New Zealand}\\
%       \email{trovato@corporation.com}
% 2nd. author
%\alignauthor
%G.K.M. Tobin\titlenote{The secretary disavows
%any knowledge of this author's actions.}\\
%       \affaddr{Institute for Clarity in Documentation}\\
%       \affaddr{P.O. Box 1212}\\
%       \affaddr{Dublin, Ohio 43017-6221}\\
%       \email{webmaster@marysville-ohio.com}
% 3rd. author

\maketitle
\begin{abstract}
Networks with single points of failure are particularly susceptible to
adversarial faults, in which an attacker targets nodes strategically.
Centralized network architectures necessarily exhibit this vulnerability,
leading to a growing popularity in decentralized architectures and protocols.
However, centralized network structure can arise even when protocols are
decentralized.
While based on decentralized protocols, the Internet and World-Wide Web have
been shown both theoretically and historically to be highly susceptible to
adversarial faults, in part due to emergent, structural centralization.
Existing network trust models, such as web of trust, fail to adequately address
network structure. We develop a partial trust model that incorporates network
structure and which makes weaker, more realistic transitivity assumptions than
web of trust. We show that the partial trust model, when combined with
concurrent multipath routing, allows standard fault tolerance techniques to be
applied to communication across complex networks. We also provide a specific
algorithm for implementing this scheme on the butterfly network topology.
When network topology can be dictated, these results can be used to create
scalable, attack-tolerant infrastructures. More generally, our results provide
a formalism for evaluating the effects of network structure on adversarial
fault tolerance.
\end{abstract}

%
% The code below should be generated by the tool at
% http://dl.acm.org/ccs.cfm
% Please copy and paste the code instead of the example below. 
%
\begin{CCSXML}
<ccs2012>
<concept>
<concept_id>10002978.10002986</concept_id>
<concept_desc>Security and privacy~Formal methods and theory of security</concept_desc>
<concept_significance>500</concept_significance>
</concept>
<concept>
<concept_id>10003033.10003034</concept_id>
<concept_desc>Networks~Network architectures</concept_desc>
<concept_significance>500</concept_significance>
</concept>
<concept>
<concept_id>10011007.10010940.10010971.10010972.10010540</concept_id>
<concept_desc>Software and its engineering~Peer-to-peer architectures</concept_desc>
<concept_significance>500</concept_significance>
</concept>
</ccs2012>
\end{CCSXML}

@@

%
% End generated code
%

%
%  Use this command to print the description
%
\printccsdesc

% We no longer use \terms command
%\terms{Theory}

\keywords{networks; decentralization; fault tolerance; routing; multipath routing; adversarial faults; information security}

@@

\begin{figure}
\centerline{\includegraphics[width=2.12in,height=1.46in]{fig-alice_trusted_neigh2}}
\caption{
Illustration of the {\em partial trust} model.
Edges represent direct, mutual trust relationships.
Alice ($v$) trusts all nodes less than
$h$ hops away---her {\em trusted neighborhood} $T_h(v)$.
Beyond that, the nodes at distance $h$ form her {\em trust boundary} $B_h(v)$.
We assume adversaries are unable to compromise nodes in the trusted neighborhood.
By compromising all nodes in the trust boundary, an adversary can ensure that
all communications leaving Alice's trusted neighborhood are compromised.
}
\label{fig:trust-source}
\end{figure}

@@

\begin{figure}
\centerline{\includegraphics[width=3.33in,height=1.46in]{fig-bob_Alice_trusted_neigh2}}
\caption{
Partial trust model with sender (Alice) and receiver (Bob).
If disjoint paths exist connecting each node in Alice's trust boundary to
a node in Bob's,
than an adversary needs to compromise at least $|T_h(v)|$ nodes to
compromise all possible paths between Alice and Bob.
}
\label{fig:trust-source-destionation}
\end{figure}

@@

\begin{table}%
\caption{Butterfly Multipath Routing Variables\label{tab:routing}}
{
\begin{tabular}{|l|l|}
\hline
NAME & VARIABLE \\\hline
butterfly dimension & $m \in \mathbb{Z}_+$ \\\hline
node level & $l \in \mathbb{Z} : 0 \leq l < m$ \\\hline
node place within level & $z \in \mathbb{Z}_2^m$ \\\hline
trust radius & $h \in \mathbb{Z} : 1 \leq h \leq \lfloor m/2 \rfloor$ \\\hline
path index & $s \in \mathbb{Z}_2^h$ \\\hline
\end{tabular}
}
\end{table}%

@@

%ACKNOWLEDGMENTS are optional
\section{Acknowledgments}
Anonymized for blind review.

%
% The following two commands are all you need in the
% initial runs of your .tex file to
% produce the bibliography for the citations in your paper.
\bibliographystyle{abbrv}
\bibliography{paper}  % sigproc.bib is the name of the Bibliography in this case
% You must have a proper ".bib" file
%  and remember to run:
% latex bibtex latex latex
% to resolve all references
%
% ACM needs 'a single self-contained file'!
%
%
\end{document}
